---
title: "Week2 R Assignment. An Alternative to choose()"
author: "Sridhar AlwarsamyPerumalsamy"
date: "July 16, 2016"
output: html_document
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
```
 
Implement an alternative to choose() function.  n! / (( n – r)! * r!) (Combinations without Repetition)

What is Permutation and Combination.?

1.If the order doesn't matter, it is a Combination.<br>
2.If the order does matter it is a Permutation.

<u>Formulas related to permutaion and combination</u>

Permutations with Repetition <bR>
<pre>n!</pre>

Permutations without Repetition <br>
<pre> n!/(n-r)!</pre>

Combinations without Repetition. [Choose() function in R]<br>
<pre>n! / (( n – r)! * r!) </pre>

##Implement an alternative to choose() function.  n! / (( n – r)! * r!)

<pre>We name the new function as chooseCombination().</pre>

```{r  echo=TRUE}
findfact <- function(x) {
  if (x == 0 || x == 1) {
      1
  }
  else{
     x * factorial(x - 1)
  }
  }

chooseCombination <- function(numberofElements, subElements){
  #compute using the formula n! / (( n – r)! * r!).
  value= findfact(numberofElements)/(findfact(numberofElements-subElements)* findfact(subElements))
  print(paste('chooseCombination(', numberofElements, ',', subElements, '):', value))
  
}

```

<h2>Test  chooseCombination() and Verify with choose()</h2>
```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Test 
chooseCombination(10,5)
#Verify with choose()
print(paste('choose(10,5):', choose(10,5)))

#Test 
chooseCombination(20,6)
#Verify with choose()
print(paste('choose(20,6):', choose(20,6)))
#Test
chooseCombination(30,7)
#Verify with choose()
print(paste('choose(30,7):', choose(30,7)))
#Test
chooseCombination(40,8)
#Verify with choose()
print(paste('choose(40,8):', choose(40,8)))
#Test
chooseCombination(50,9)
#Verify with choose()
print(paste('choose(50,9):', choose(50,9)))

```



